<span style="color:red;">Building a house with<br />Advanced Normalization Tools (*ANTs*)</span>

### 2014-09-03 ants2015build.Rmd
WIP: regular update

@@

@@

Only change to the command call is an additional '-c WM[7]' which means "combine
the 7<sup>th</sup> prior, i.e. lesion, to the white matter for cortical thickness calculation."
# Wrap-up & Conclusions

>>>>

## Templates unlock modalities

![](figures/ptbp2.png)

@@

# ANTs versus Freesurfer:<br />  Quantifying *life span* brain health

## "Big data" problem from public resources
![](./figures/lifebrains.jpg)

TOT, NKI, IXI, Oasis, ADNI ... several thousand images

## ANTs versus Freesurfer:<br />  Quantifying *life span* brain health

* Freesurfer is the historical standard for measuring cortical thickness

* instead of using surfaces to measure cortical thickness, we use the image space *DiReCTly*

* [see this section of a different talk](http://stnava.github.io/ANTsTalk/#/putting-it-all-together-can-we-quantify-life-span-brain-health-in-individuals-and-in-populations)

* and this "big data" paper: [Large-scale evaluation of ANTs and FreeSurfer cortical thickness measurements](http://www.ncbi.nlm.nih.gov/pubmed/24879923)

* comparison of prediction from automated cortical thickness measurement from 4 public datasets

* $>$ 1200 subjects, age 7 to over 90 years old

* *hint*: ANTs thickness measurements have higher prediction accuracy relative to Freesurfer ( implying we extract more information from the data )

* ANTs methods consistently improve statistical power [eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/24687814), [syn](http://www.ncbi.nlm.nih.gov/pubmed/?term=syn+epstein+avants), [itkv4](http://www.ncbi.nlm.nih.gov/pubmed/24817849) ... also, see [Schwarz CG, et al.](http://www.ncbi.nlm.nih.gov/pubmed/24650605) re: TBSS and related work in fMRI [Miller, PNAS](http://www.ncbi.nlm.nih.gov/pubmed/15980148), [Azab, et al in Hippocampus](http://www.ncbi.nlm.nih.gov/pubmed/24167043).

## Cortical thickness estimation

<div align="center"><img height="250" src="./figures/corticalThicknessEstimation.png" frameborder="0"></img></div>

In contrast to FreeSurfer which warps coupled surface meshes to segment the gray matter, *ANTs* diffeomorphically registers the white matter to the combined gray/white matters while simultaneously estimating thickness.

# New work

@@

Only change to the command call is an additional '-c WM[7]' which means "combine
the 7<sup>th</sup> prior, i.e. lesion, to the white matter for cortical thickness calculation."

# Wrap-up & Conclusions
